Towards practical dynamic induction control of wind farms: analysis of optimally controlled wind-farm boundary layers and sinusoidal induction control of first-row turbines

### 2018-02-14 draft.tex
Small aesthetics fix

\subsection{Case setup}
The wind farm considered in MM17 has an aligned pattern of 12 rows by 6 columns, with 6 rotor diameters spacing in axial and tranversal directions. The flow is simulated on a domain of $10 \times 3.6 \times 1$ km$^3$, discretized on a simulation grid of $384 \times 192 \times 144$ grid points. A snapshot of the streamwise velocity field is shown in Fig. \ref{fig:flowfield_MM17}. The wind farm was controlled over a total of $N_A = 15$ time windows with a prediction horizon $T = 240 s$ and a flow advancement time of $T_A = T/2 = 120 s$, resulting in a total control time $T_{\rm tot} = N_A T_A = 30$ minutes.

@@

A conventionally (greedily) controlled wind farm with steady $C_T' = 2$ (corresponding to the Betz limit in momentum theory) was defined as a reference case. Several different optimal control cases were defined, based on the wind-turbine response time $\tau = $0, 5, or 30 s (instantaneous, fast, or slow response, see Eq. \ref{eq:ctihat_constraint}) and the maximal thrust coefficient $C_{T,\text{max}}' = 2$ or 3 (underinductive or overinductive, see Eq. \ref{eq:boxct_constraint}). Cases are denoted as C<X>t<Y>, where X and Y represent $C_{T,\text{max}}'$ and $\tau$ respectively, e.g. C3t30  for the case with $C_{T,\text{max}}' = 3$ and $\tau = 30$ s.

>>>>

\subsection{Case setup}
The wind farm considered in MM17 has an aligned pattern of 12 rows by 6 columns, with 6 rotor diameters spacing in axial and tranversal directions. The flow is simulated on a domain of $10 \times 3.6 \times 1$ km$^3$, discretized on a simulation grid of $384 \times 192 \times 144$ grid points. A snapshot of the streamwise velocity field is shown in Fig. \ref{fig:flowfield_MM17}. The wind farm was controlled over a total of $N_A = 15$ time windows with a prediction horizon $T = 240$ s and a flow advancement time of $T_A = T/2 = 120$ s, resulting in a total control time $T_{\rm tot} = N_A T_A = 30$ minutes.

@@

A conventionally (greedily) controlled wind farm with steady $C_T' = 2$ (corresponding to the Betz limit in momentum theory) was defined as a reference case. Several different optimal control cases were defined, based on the wind-turbine response time $\tau = $ 0, 5, or 30 s (instantaneous, fast, or slow response, see Eq. \ref{eq:ctihat_constraint}) and the maximal thrust coefficient $C_{T,\text{max}}' = 2$ or~3 (underinductive or overinductive, see Eq. \ref{eq:boxct_constraint}). Cases are denoted as C<X>t<Y>, where X and Y represent $C_{T,\text{max}}'$ and $\tau$ respectively, e.g. C3t30  for the case with $C_{T,\text{max}}' = 3$ and $\tau = 30$ s.
